### 2024-07-21 law-firms-names/Paper.Rmd
Add results for neightboring regions and regions distance, #5

---
title: "Spatial Analysis of Russian Law Firms Naming"
author: "Pavel Syomin¹"
output:
  word_document:
    reference_doc: "journal-article/reference.docx"
bibliography: "journal-article/refs.bib"
csl: "journal-article/apa.csl"
link-bibliography: False  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<div custom-style="Affiliation">

¹Perm State University, Geographical faculty, Department of social and economic geography, Perm, Russia; e-mail: ntsp\@ya.ru

</div>

<div custom-style="Abstract">

**Abstract:** text.

</div>

<div custom-style="Keywords">

**Keywords:** naming; law firms; text embeddings; economic regions. 
</div>

# 1. Introduction

Geography of services, sometimes referred to as geography of service sector, is one of the essential parts of socio-economic geographical studies in Russia. Its history spans for several decades starting from the 1960s. Geography of services has economic and social dimensions, where the former is concentrated on the business aspects of the services, while the latter is focused on the issues of human well-being arising from the spatial structure of the relevant services [@Tkachenko2016]. Existing scientific literature on the geography of services in Russia covers a broad range of topics, e.g. education [@Shulgina2019], car rental [@Zyrianova2018], catering [@Preobrazhenskiy2018], medical care [@Kazantcev2022; @Panin2023; @Nikoloski2024], internet access [@Nagirnaya2015; @Zemtsov2022]. However, research on some problems is limited, with legal services being one of the notable examples of such a problem [@Tkachenko2016; @Moiseeva2016]. Despite the lack of attention from geographers, spatial aspects of law firms activity worth investigating for the several reasons. First, legal services can be categorized as business and producer services, acting as a representative case, and this category of services is important for the economic development in general, both in national or regional scale [@Hansen1993; @Faulconbridge2019]. Next, despite their relatively small direct economic impact, they have a great indirect importance as the intermediaries and helpers that contribute to the rule of law, social order, stability and predictability of social relations. Third, for regular citizens access to legal aid is important for the protection of human rights and ensuring the social justice, and in this context, the spatial aspects of law services are on par with the spatial issues of medical care [@Blacksell1988; @Blacksell1990].

Geographical research of services may focus on a variety of subjects. Some classical pathways of such research include analysis of centers and systems of service or of consumers' behavior, needs and demands, including estimation of influencing factors, investigation on the actual level of services provision, applied scientific work related to the management of social infrastructure [@Tkachenko2016]. Studies of firm names, sometimes also referred to as company names, brand names or just brands, is relatively unusual yet potentially fruitful method in the geography of services. Firm names are designed to distinguish the business from the competitors, to make an emphasis on the field of activity or its geographical area, inform about services supplied by a provider and corresponding benefits. Having these functions, brands convey a substantial portion of information in a short text message. Such information may be useful to discover the city's business landscape and consumer's perception of a particular city with its characteristic services [@Raento2001], analyze the trends common to a specific industry in a region [@Marjavaara2022] or the role of place as reflected in the toponyms in the business development and consumer attitudes [@Peluso2012; @Zhang2014; @Erdogan2016; @Noorda2019]. Company names represent the characteristics of businesses and thus may act as “meta-proxy” for a bulk of intertwined economic metrics. Such a complex nature makes them suitable for regions identification, especially in the case of vernacular regions [@Reed1976; @Liesch2015; @Vukosav2016; @Holtkamp2018]. Other interactions between places and brands, e.g. the contribution of commercial branding to place branding [@Florek2013] or its compliance with the latter [@BassolsiGardella2023] may also be of interest.

There are thousands of law firms in Russia [@Moiseeva2016]. Their names are likely to reflect some properties of local legal services market. The area of Russia is comprised of regions (constituent entities of the federation) that provide some sort of a commonly used spatial unit for geographical studies. Besides, economic geographers split the country into 11 economic regions [@Leyzerovich2010]. Each economic regions includes several constituent entities and is characterized by internal integrity, economic links between the companies, specialization and difference from the others. It can be hypothesized that the proximity of regions, as well as internal unity and economic links within the economic regions, leads to the similarity of law firms activity and, correspondingly, to the similarity of their naming. The overall aim of this study is to check whether this is true. To achieve this goal, a few research questions are asked and then answered based on the data on law firms names. These questions, or problems, are specified below.

Question 1 (Q1) is whether the neighboring regions have more similar law firm names that regions that do not share a common border. Question 2 (Q2) is a continuous extension of Q1: whether the geographical proximity of regions has an impact on the similarity of law firm names, i.e. whether the regions that are close to each other have more similar names, and vice versa. Question 3 (Q3) moves up from the level of regions to the level of economic regions: whether names within the economic region are more similar compared to the names outside the region. Question 4 (Q4) is what naming strategies exist in Russia and how they are spatially organized. Question 5 (Q5) is a follow-up from the previous: are there strategies common or different within each economic region?

# 2. Materials and methods

## 2.1. Data

The issue of obtaining information about firm names is challenging. Even though all Russian organisations are registered in the unified state registry operated by Federal Tax Service (FTS of Russia), and an extract about a particular company from this registry can be downloaded online by any person free of charge, there is no straightforward way to get names of all companies from the registry at once without paying a considerable amount of money and without negotiating a contract with the responsible government body. There are a few commercial firms that re-cell the data from the registry of companies, but the prices are substantial. To overcome these problems, a Unified state registry of small and medium-sized businesses (SMB registry) was used. This registry has been maintained since 2016 according to the Article 4.1 of Federal Law of July 24, 2007 No 209-FZ “On the development of small and medium-sized businesses in the Russian Federation”. All the companies and individual entrepreneurs that have a yearly revenue below 2 billion roubles and an average yearly number of employees below 250 are automatically included in the SMB registry without any action required on their side. In contrast to the main registries of companies and entrepreneurs, SMB registry can be fully downloaded at the FTS open data portal free of charge, as well as the monthly history of its updates since the beginning of the operation. Thus, this registry can be treated as the most comprehensive free data source with the information about Russian business entities (organisations and individuals). The downloadable version of the registry includes, in particular, firm names, addresses of registration (up to a settlement), and codes of activity kinds according to the All-Russia Classifier of Kinds of Economic Activity. Large firms are not present in the registry, so some data is missing. However, the majority of commercial law firms in Russia (more than 75%) can be categorized as small and medium-sized businesses and are included in the registry, so the availability of information is relatively high, and it can be used for trustworthy conclusions.

## 2.2. Methods

### 2.2.1. FTS data processing

SMB registry dumps from FTS website have a large volume (≈200 Gb in total) and a complex structure: each dump is an archive of several thousand XML files, and each XML file contain 900 records with various information about organisations and individuals. Dumps are monthly, resulting in ≈90 archives for the period from 2016 to the present. If unpacked, all archives would occupy more than 2 Tb of disk space, and the extraction and preprocessing of such volume of data would take a large time. It should be noted, though, that the majority of information is redundant for the task in hand, because it is duplicated due to data publication specific (each archive contains a full copy of the registry, and if nothing has changed during the month, the data records will be merely the same) and because only the data about law firms is required, while the registry holds information about all the other firms as well. To extract necessary data from the raw archives, an open-source Python command-line tool was developed named ru-smb-companies. The main stages of data extractions are outlined in the next paragraph, while for the complete information about data processing workflow readers may refer to the source code of the program.

FTS data processing took several steps. First, all source archives available at the time of research (November 2023) were downloaded  from FTS servers and stored both locally and in the cloud. Next, information about law firms was extracted from each archive to a CSV file. Extracted attributes include company or person name, address of incorporation (region, district, city, settlement), taxpayer ID, main activity code and some other properties. After this, CSV tables were combined into one table, deduplicated, and raw addresses were normalized and geocoded to fix the inconsistency in location names and add geographical coordinates. Finally, the resulting table was transformed in a panel view so that each row represents one business entity at a given year. The output table contains data about ≈ 30, 000 law firms for 2016–23.

### 2.2.2. Firm names processing

A major challenge regarding the methods of this study is the working with names. The objectives of the research imply that names should be grouped and compared in some way. This can easily be accomplished with numbers, but firm names are just short text sequences. Of course, a human can easily say whether two names are similar or not and classify them. However, the human-based approach does not scale well, and the quantity of names requires automation. There are several traditional techniques allowing us to compare text strings. For example, edit distance calculates the number of atomic changed required to turn one string to another, and the edit distance between “cat” and “car” is 1, while the edit distance between “car” and “karst” is 3. Another method named n-gram similarity splits the strings into subsequences, or tokens, and finds the number of common tokens, so that “law company” and “law bureau” are more close to each other than “law bureau” and “juridical center”. Despite their simplicity, they also have a significant disadvantage: they cannot account for the intrinsic variability and flexibility of language and do not consider the meaning of the words and phrases rather than their formal representation. For instance, a human understands that “law company” and “legal organisation” mean almost the same, while edit distance between these strings is high, and n-gram similarity is low. A modern method called text embeddings (sometimes referred to as vectors) can deal with this issue and therefore it is used for this research.

Text embedding, or vector, is a numeric representation of a word, sentence or a document usually designed to catch the meaning of the text. An embedding typically looks like just a sequence of decimals with fixed length, i.e. the count of elements in this sequence does not depend on the length of the input text, so that a short sentence or an entire paragraph are represented as a sequence of, say, 256 numbers. Vectors allow simple computations to find out whether they are more or less similar to each other, and the similarity of vectors corresponds to the similarity of texts. Thus, by computing a mathematical distance between embeddings, one can conclude about the semantic distance between texts. This is right the case of firm names comparison, similarity, and grouping.

There are various methods of obtaining embeddings for different texts, e.g. Word2Vec, GloVe, FastText. The newest GPT-based pretrained large language models such as ChatGPT are also capable of producing text vectors. For this study, embeddings from YandexGPT model were used. These embeddings were obtained for each unique firm name via public API of the model. The vector dimensionality is 256, i.e. each vector is a sequence of 256 numbers. All the concrete hypothesis testing techniques outlined in the next subsection are based on the use of these vectors.

### 2.2.3. Hypothesis testing

To answer Q1, firm names vectors by each region were averaged so that all names of a region are represented with a single vector that equals to the mathematical mean of all firm names vectors within this region. All regions are divided into two groups depending on the presence of common border between them. Pairwise distances between all the regions are calculated, and then median distance between regions in each of two groups is calculated. The results are additionally visualized as a box plot. It is expected that median distance between neighboring regions is smaller than median distance between regions that do not have a same border.

The similar technique is used for Q2. Again, the mean vector of all firm names for each region is computed, and pairwise semantic distance between regions is calculated. Then, a geographical distance between the centroids of regions is also measured. A correlation between geographical distance and semantic distance is computed, and the result is plotted. It is expected that the coefficient of correlation is positive.

Q3 also builds upon the pairwise semantic distances between regions. After these distances are found out, regions are grouped by economic regions. For each economic region, two metrics are calculated: the first is a median distance between regions within this econoimic region, and the second is a median distance between regions within and without this economic region. It is expected that within-median-distance is smaller that beyond-median-distance. The results are additionally illustrated on a boxplot.

Q4 and Q5 follow a slightly different methodics. First, all firm names are clustered with KMeans algorithm (number of clusters is 50). After clustering, a random sample of names from each cluster is taken, and these names are manually checked, described and tagged with the labels of more broad groups. Then these manually defined groups are assigned to names using clusters as links between groups and individual names. The number of names belonging to each group in each region is calculated, and the results of this calculation are mapped on a tile-grid map of Russia to analyze the spatial properties of grouping. In this way, Q4 is processed. For Q5, the regions are marked with the label of the most popular group, and the number of regions with different groups within an economic region is counted. It is expected that each economic regions is characterized with only one majority group. It may be the same as the group for another economic region, but a small if any variation is expected within an economic region to prove its integrity. Also, in general it is expected that there are several clear and meaningful firm naming groups, or naming strategies, and that these groups may have (or not) some clear geographical patterns.

### 2.2.4. Other important considerations

The time range of the source data is from 2016 to 2023. Only the firms that have existed for at least 3 years are included in the analysis. Only organizations are studied, while individual entrepreneurs are omitted, because they do not have firm names. Firm names are preprocessed to remove any parts pointing to the legal form of the business (e.g. limited liability company or public stock company), because these parts are common to the majority of names and thus do not add anything valuable. Law firms are selected by filtering using the following condition: main activity code equals 69.10 (activity in the area of law according to All-Russia Classifier of Kinds of Economic Activity). This filtering technique is derived from @Moiseeva2016.

# 3. Results and discussion

## 3.1. Semantic distance between heighboring regions is smaller

Figure 1 shows the median semantic distance between law firm names of neighboring regions versus the same of regions that do not have a common border. Despite the difference in medians is relatively small, it does exist, and the overall distribution of values for non-neighboring regions is shifted to the area of higher distances compared to the distribution of values for bordering regions. Thus, the hypothesis from Q1 turns out to be true: neighboring regions are indeed closer to each other in terms of semantic distances between their law firm names.

```{r fig-1-neighbors, fig.cap="Figure 1. The relationship between neightboring status of regions and semantic distance between names of law firms incorporated in these regions", fig.height=3}
neighbor_plot
```
## 3.2. The larger the geographical distance, the larger is semantic distance

Figure 2 shows the continuous analog of Figure 1, i.e. the scatter plot of geographical versus semantic distance between regions according to their law firms names. The observed correlation is weak yet positive. Besides, there are two clusters of points. Thus, for Q2 the answer is partial: there is a positive relationship between the geographical distance and semantic distance of law firm names between regions, but the observed correlation is weak, and also there is a minor group of region pairs that seems to have no such correlation at all.

```{r fig-2-distance-plot, fig.cap="Figure 2. Relationship between geographical distance between regions and semantic distance between names of law firms incorporated in these regions", fig.height=3}
distance_plot
```

# 4. Conclusion

<div custom-style="References-title">References</div>

<div id="refs"></div>

### 2024-07-21 law-firms-names/journal-article/Script.R

@@ -9,6 +9,8 @@ library(stringr)
 library(tidyr)
 library(units)
 
+sf_use_s2(FALSE)
+
 data <- read_csv(here("../../ru-smb-companies/legal/panel.csv"))
 er <- read_csv(here("journal-article", "economic-regions.csv"))
 tiles <- read_csv(here("common", "russia-tiles.csv"))
@@ -117,7 +119,6 @@ region_vectors <- vectors %>%
   filter(cnt > quantile(cnt, .05)) %>% 
   select(-cnt)
 
-sf_use_s2(FALSE)
 neighboring_regions <- as_tibble(cbind(
   iso = ru$shapeISO,
   as.data.frame(st_intersects(ru, ru, sparse = FALSE, remove_self = TRUE))
@@ -173,17 +174,59 @@ region_distances %>%
   ggplot(aes(x = dist)) +
   geom_freqpoly()
 
-ggplot(region_names_distances, aes(x = is_neighbor, y = namedist)) +
-  geom_boxplot()
+neighbor_plot <- region_names_distances %>% 
+  ggplot(aes(x = namedist, y = is_neighbor)) +
+  geom_boxplot() +
+  geom_text(
+    aes(
+      label = after_stat(paste("M == ", round(xmiddle, 2))),
+      x = stage(namedist, after_stat = xmiddle)),
+    stat = "boxplot",
+    vjust = -.75,
+    parse = TRUE,
+    size = 3,
+    family = "Segoe UI Semilight",
+    angle = 90
+  ) + 
+  scale_y_discrete(labels = c("Other\nregions", "Neighboring\nregions")) + 
+  labs(
+    x = "Euclidean distance between region vectors",
+    y = ""
+  ) +
+  theme_bw(base_family = "Segoe UI Semilight", base_size = 9)
+neighbor_plot
 
 t.test(namedist ~ is_neighbor, data = region_names_distances)
 wilcox.test(namedist ~ is_neighbor, data = region_names_distances)
 region_names_distances %>% group_by(is_neighbor) %>% summarise(m = median(namedist))
 
-ggplot(region_names_distances, aes(x = geo_distance, y = namedist)) +
-  geom_point()
+distance_plot <- region_names_distances %>% 
+  ggplot(aes(x = geo_distance, y = namedist)) +
+  geom_point(color = "grey50", size = 1, shape = 21) +
+  geom_smooth(method = "lm", se = FALSE) +
+  annotate(
+    "label", 
+    x = as_units(Inf, "km"),
+    y = Inf, 
[…]

### 2024-07-22 fts-open-data-in-economic-geography/helpers/Plots.R
Fix an issue with maps, make minor edit in en biblio, #5

@@ -74,7 +74,9 @@ regions_plot_agri_forestry <- rsmp_data %>%
     end_date >= "2021-12-31",
     !is.na(ac_type)) %>% 
   count(region, ac_type) %>% 
-  left_join(regions, by = c("region" = "name")) %>% 
+  right_join(regions, by = c("region" = "name")) %>% 
+  pivot_wider(names_from = ac_type, values_from = n) %>% 
+  pivot_longer(cols = c(labels[4], labels[5]), names_to = "ac_type", values_to = "n") %>% 
   st_as_sf() %>% 
   ggplot() +
   geom_sf(aes(fill = n / 1000), linewidth = .05) +

### 2024-07-22 law-firms-names/Paper.Rmd
Add economic regions comparison and naming strategies, #5

@@
 ```
+
 ## 3.2. The larger the geographical distance, the larger is semantic distance
@@
 
+## 3.3. Semantic distance within economic regions is smaller
+
+Figure 3 shows the comparison of distances between law firm names within economic regions and outside them.
+The results are mixed.
+In some cases, the distance between regions belonging to the same economic region is a bit smaller than the distance between regions belonging to an economic region and other regions that do not belong to this economic region.
+However, there are several economic regions where this tendency does not holds.
+In addition, it looks like that the overall shape of semantic distance distributions in these economic regions imply that there are internal subdivisions within this economic region, and thus it seems to be not as united and integral as it is theoretically suggested.
+This observation has a potential to be quite intriguing for checking the validity of economic regions classification in Russia.
+Nevertheless, its relative importance in the context of regioning task is quite low, and thus there is no need to make provisions on classification updates right now.
+
+```{r fig-3-economic-regions-distance, fig.cap="Figure 3. Semantic distance between regions within and outside economic regions", fig.height=4}
+economic_regions_distances
+```
+
+## 3.4. There are three primary naming strategies: form-, field-, service-based
+
+Manual analysis of clustered names samples shows that all the law firm names, except for uncategorized, can be grouped into three generic catgories: form-based, field-based, service-based names.
+*Form-based names* are focused on the organizational form, or type, of business, company or firm and usually include the words like “company”, “partnership”, “corporation”, “alliance”, “center”, “bureau”.
+In contrast, *field-based names* point to the field of company's activity, i.e.
+law, and thus are usually based on law-related words such as “legal”, “juridical”, “lex”.
+*Service-based names* mention the service nature of the business in general by using words “services” or address the specific kinds of services or areas of related business, e.g.
+“consulting”, “analytics”, “expertise”, “bankruptcy”, “arbitrazh”, “accounting”, “finance”, “real estate”.
+As seen in Figure 4, field-based and service-based naming strategies dominate over form-based, sharing in total more than 80% of all strategical law firm names in the majority of regions.
+Consequently, all the regions may be divided into two broad groups: either with field-based naming of law firms or with service-based naming of law firms.
+The spatial patterns of these grouping are nevertheless obscure, with no clear geographical tendencies, and the overall spatial distribution of these naming strategies looks random.
+
+```{r fig-4-naming-strategies, fig.cap="Figure 4. Map of naming strategies by regions and economic regions"}
+
+```
+
 # 4. Conclusion

### 2024-07-22 law-firms-names/journal-article/Script.R

@@ -165,10 +165,33 @@ region_names_distances <- region_names_distances %>%
 region_distances_stat <- region_distances %>% 
   group_by(economic_region, within) %>% 
   summarise(dist = median(dist))
-region_distances %>% 
-  ggplot(aes(x = economic_region, y = dist, color = within)) +
+
+economic_regions_distances <- region_distances %>% 
+  ggplot(aes(x = within, y = dist)) +
   geom_violin(draw_quantiles = c(.5)) +
-  geom_jitter(width = .1, size = .2)
+  geom_jitter(size = 1, shape = 21, alpha = .3) +
+  geom_text(
+    aes(
+      y = stage(dist, after_stat = 0),
+      label = after_stat(paste("M == ", round(middle, 2)))
+    ),
+    stat = "boxplot",
+    vjust = -.25,
+    parse = TRUE,
+    size = 3,
+    family = "Segoe UI Semilight",
+  ) +
+  scale_x_discrete(
+    name = "Distance type",
+    labels = c("Inside–outside", "Within")
+  ) +
+  facet_wrap(vars(economic_region), ncol = 3) +
+  labs(
+    y = "Distance between regions"
+  ) +
+  theme_bw(base_family = "Segoe UI Semilight", base_size = 9)
+economic_regions_distances
+
 arrange(region_distances, -dist)
 region_distances %>% 
   ggplot(aes(x = dist)) +
@@ -248,7 +271,8 @@ count(clustered, region, group) %>%
   facet_wrap(vars(group), ncol = 2)
 
 # Field-based vs service-based names
-count(clustered, region, group) %>% 
+naming_strategies <- clustered %>% 
+  count(region, group) %>% 
   filter(group != "Misc") %>% 
   group_by(region) %>% 
   arrange(-n) %>% 
@@ -266,12 +290,67 @@ count(clustered, region, group) %>%
   right_join(er) %>% 
   drop_na(main_group) %>% 
   ggplot(aes(x = col, y = -row)) +
-  geom_tile(aes(fill = economic_region, width = 1, height = 1, color = main_group), linewidth = 2) +
-  geom_text(aes(x = col - .25, y = -row + .25, label = code_en), size = 3, hjust = 0) +
-  geom_text(aes(x = col - .3, y = -row, label = Law), shape = 21) +
-  geom_text(aes(x = col - .3, y = -row - .3, label = Service), shape = 21) +
[…]

### 2024-07-24 law-firms-names/Paper.Rmd
Add a map and a paragraph about naming strategies in economic regions, add conclusion, remove useless code, #5

@@
 knitr::opts_chunk$set(echo = TRUE)
+```
+
+```{r imports, cache=TRUE, include=FALSE}
+library(here)
+source(here("journal-article", "Script.R"))
 ```
@@
 Consequently, all the regions may be divided into two broad groups: either with field-based naming of law firms or with service-based naming of law firms.
-The spatial patterns of these grouping are nevertheless obscure, with no clear geographical tendencies, and the overall spatial distribution of these naming strategies looks random.
+The spatial patterns of these grouping are nevertheless obscure, with no clear geographical tendencies, and the overall spatial distribution of these naming strategies looks random, except for the prevalence of service-based names in the European South.
 
 ```{r fig-4-naming-strategies, fig.cap="Figure 4. Map of naming strategies by regions and economic regions"}
-
+naming_strategies
 ```
 
+## 3.5. Naming strategies are not consistent over economic regions
+
+From Figure 4 one can easily conclude that few economic regions are characterized by a consistent naming strategy.
+In Volga-Vyatka region, law-based strategy is the most popular one among all the regions, except for the Republic of Mari El.
+In Volga and North Caucasus, service-based strategy prevails in the majority of regions.
+The same also holds for the Eastern Siberia, though the large size of the Krasnoyarsk territory, the only exception, overweights the quantity of regions with service-based stratery, thus the economic region in general can not be treated the same as Volga and North Caucasus.
+All the other economic regions are characterized by a blend of law firms naming strategies.
+
 # 4. Conclusion
+
+The results of the research are mixed.
+On the other hand, several hypothesis have been proven: law firm names in neighboring regions are more similar than law firm names in non-neighboring regions; the smaller the geographic distance between regions, the more similar the law firm names; law firm names within an economic region are typically more similar compared to the law firm names outside an economic regions.
+On the other hand, the difference in the metrics of similarity is relatively small in all these cases, as well as the correlation coefficient, thus it should be noted that although the hypothesized phenomena do exist, their magnitude is weak.
+
+There are three primary law firm naming strategies: form-based, law-based, service-based.
+The form-based strategy is in a minority, accounting for ≈10% of all the names.
+Two other strategies share the remaining majority, and in some regions, law-based naming prevails, while in the others, service-based naming is more common.
+Service-based law firms naming is a dominant strategy in the majority of regions in the European South of Russia.
+Other geographical regularities regarding the law firm naming are unclear.
+Economic regions are typically characterized by a mixture of naming strategies, expect for Volga-Vyatka with dominating law-based strategy, and Volga with North Caucasus with service-based strategy prevailing in the majority of constituting regions.
+
+The contribution of this study is mostly theoretical and methodological.
+It emphasizes the importance of firm names as the source of information for business- and economy-related research.
+It also proposes a technique of using modern natural language processing (NLP) solutions based on artificial neural networks for integral analysis of company naming in a geographical context, as well as the usage of disaggregated administrative open data for a spatial analysis.
+The results argue for the effect of geographical proximity and neighboring on the similarity of economical and (to some extent) cultural properties of the territories.
+They also generally support the widely used classification of economic regions in Russia, though noticing a few weak places where there is an internal heterogenity within an economic region.
+The study also offers an example of semi-automated company names classification in a particular field of economic activity and points at some kind of geographical differentiation in the naming strategies, that may be subject to further spatial analysis.
 

### 2024-07-24 law-firms-names/journal-article/Script.R

@@ -162,17 +162,13 @@ region_names_distances <- region_names_distances %>%
   left_join(neighboring_regions, by = c("iso_code" = "iso", "iso_code_2" = "iso_2")) %>% 
   left_join(geo_distances, by = c("iso_code" = "iso", "iso_code_2" = "iso_2"))
 
-region_distances_stat <- region_distances %>% 
-  group_by(economic_region, within) %>% 
-  summarise(dist = median(dist))
-
-economic_regions_distances <- region_distances %>% 
-  ggplot(aes(x = within, y = dist)) +
+economic_regions_distances <- region_names_distances %>% 
+  ggplot(aes(x = within, y = namedist)) +
   geom_violin(draw_quantiles = c(.5)) +
   geom_jitter(size = 1, shape = 21, alpha = .3) +
   geom_text(
     aes(
-      y = stage(dist, after_stat = 0),
+      y = stage(namedist, after_stat = 0),
       label = after_stat(paste("M == ", round(middle, 2)))
     ),
     stat = "boxplot",
@@ -192,10 +188,6 @@ economic_regions_distances <- region_distances %>%
   theme_bw(base_family = "Segoe UI Semilight", base_size = 9)
 economic_regions_distances
 
-arrange(region_distances, -dist)
-region_distances %>% 
-  ggplot(aes(x = dist)) +
-  geom_freqpoly()
 
 neighbor_plot <- region_names_distances %>% 
   ggplot(aes(x = namedist, y = is_neighbor)) +
@@ -251,106 +243,81 @@ distance_plot
 
 cor.test(~namedist+geo_distance, data = filter(region_names_distances))$estimate
 
-# Look at distribution by various classes
-count(clustered, tag, sort = TRUE)
-count(clustered, group, sort = TRUE)
-count(clustered, strategy, sort = TRUE)
-count(clustered, western, sort = TRUE)
-
 # Tile grid map of regions by naming group
-count(clustered, region, group) %>% 
-  filter(group != "Misc") %>% 
-  group_by(region) %>% 
-  summarise(group = group, share = n / sum(n)) %>% 
-  right_join(tiles, by = c("region" = "name")) %>% 
-  drop_na(share) %>% 
-  ggplot(aes(x = col, y = -row)) +
-  geom_raster(aes(fill = share)) +
-  geom_text(aes(label = code_en), size = 3) +
[…]

### 2024-07-24 law-firms-names/Paper.Rmd
Add abstract, make minor fixes, #5

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(
+  warning = FALSE, 
+  message = FALSE, 
+  echo = FALSE, 
+  fig.width = 4.96, 
+  fig.id = FALSE,
+  dpi = 300)
 ```
@@
 
-**Abstract:** text.
+**Abstract:** the research is focused on integral analysis of law firm names in Russia and its geographical aspects.
+The main problem of the study is to find out whether several spatial relations between subdivisions of the country, namely neighboring, proximity, and belonging to an economic region, are reflected in law firm naming, and how law firm naming depends on these relations.
+To conduct the analysis, data about law firm names is extracted from the open dumps of the state small and medium-sized businesses registry.
+Law firm names are converted into numeric vectors using YandexGPT embeddings, then clustered with KMeans method, and manually grouped to detect main naming strategies.
+Numeric representations of law firm names within each country's subdivision are averaged to get a regional embedding, and then law firm names of the regions are compared using regional embeddings.
+It is found out that regions that are geographically closer to each other or have a common border tend to have slightly more similar law firm names.
+In addition, regions belonging to the same economic region have more similar law firm names either.
+There are three main law firms naming strategies: form-based, law-based, service-based.
+Volga and North Caucasus economic regions are characterized by the prevalence of service-based strategy, and Volga-Vyatka economic region has a law-based strategy, while other territories have mixed naming strategies.
+The results of the study support the existing widely used classification of economic regions in Russia and argue the impact of neighboring, proximity, and links on the economic and cultural properties of the territories.
+The administrative open data processing techniques, as well as methods of working with firm names based on neural networks proposed in this paper may be used by other economic geographers for their research purposes.
 
@@
 **Keywords:** naming; law firms; text embeddings; economic regions.
+
 </div>

### 2024-07-27 law-firms-names/Paper.Rmd
Edit introduction, #5

@@
 ---
-title: "Spatial Analysis of Russian Law Firms Naming"
+title: "Spatial Analysis of Russian Law Firm Names"
 author: "Pavel Syomin¹"
@@
 
-**Keywords:** naming; law firms; text embeddings; economic regions.
+**Keywords:** firm names; law firms; text embeddings; economic regions, text similarity.
 
@@
 
-Geography of services, sometimes referred to as geography of service sector, is one of the essential parts of socio-economic geographical studies in Russia.
-Its history spans for several decades starting from the 1960s.
-Geography of services has economic and social dimensions, where the former is concentrated on the business aspects of the services, while the latter is focused on the issues of human well-being arising from the spatial structure of the relevant services [@Tkachenko2016].
-Existing scientific literature on the geography of services in Russia covers a broad range of topics, e.g.
-education [@Shulgina2019], car rental [@Zyrianova2018], catering [@Preobrazhenskiy2018], medical care [@Kazantcev2022; @Panin2023; @Nikoloski2024], internet access [@Nagirnaya2015; @Zemtsov2022].
-However, research on some problems is limited, with legal services being one of the notable examples of such a problem [@Tkachenko2016; @Moiseeva2016].
-Despite the lack of attention from geographers, spatial aspects of law firms activity worth investigating for the several reasons.
-First, legal services can be categorized as business and producer services, acting as a representative case, and this category of services is important for the economic development in general, both in national or regional scale [@Hansen1993; @Faulconbridge2019].
-Next, despite their relatively small direct economic impact, they have a great indirect importance as the intermediaries and helpers that contribute to the rule of law, social order, stability and predictability of social relations.
-Third, for regular citizens access to legal aid is important for the protection of human rights and ensuring the social justice, and in this context, the spatial aspects of law services are on par with the spatial issues of medical care [@Blacksell1988; @Blacksell1990].
+The geography of services, also known as the geography of the service sector, is a crucial component of geographical studies in Russia.
+This field has a history spanning several decades, with origins dating back to the 1960s.
+The geography of services has two distinct dimensions: economic and social.
+The former is primarily concerned with the business aspects of the services, while the latter addresses the implications for human well-being arising from the geographical organisation of services [@Tkachenko2016].
+The existing scientific literature on the geography of services in Russia covers a broad range of topics, including education [@Shulgina2019], car rental [@Zyrianova2018], catering [@Preobrazhenskiy2018], medical care [@Kazantcev2022; @Panin2023; @Nikoloski2024], and internet access [@Nagirnaya2015; @Zemtsov2022].
+However, some areas remain underexplored, with legal services being one such example [@Tkachenko2016; @Moiseeva2016].
 
-Geographical research of services may focus on a variety of subjects.
-Some classical pathways of such research include analysis of centers and systems of service or of consumers' behavior, needs and demands, including estimation of influencing factors, investigation on the actual level of services provision, applied scientific work related to the management of social infrastructure [@Tkachenko2016].
-Studies of firm names, sometimes also referred to as company names, brand names or just brands, is relatively unusual yet potentially fruitful method in the geography of services.
-Firm names are designed to distinguish the business from the competitors, to make an emphasis on the field of activity or its geographical area, inform about services supplied by a provider and corresponding benefits.
-Having these functions, brands convey a substantial portion of information in a short text message.
-Such information may be useful to discover the city's business landscape and consumer's perception of a particular city with its characteristic services [@Raento2001], analyze the trends common to a specific industry in a region [@Marjavaara2022] or the role of place as reflected in the toponyms in the business development and consumer attitudes [@Peluso2012; @Zhang2014; @Erdogan2016; @Noorda2019].
-Company names represent the characteristics of businesses and thus may act as “meta-proxy” for a bulk of intertwined economic metrics.
-Such a complex nature makes them suitable for regions identification, especially in the case of vernacular regions [@Reed1976; @Liesch2015; @Vukosav2016; @Holtkamp2018].
-Other interactions between places and brands, e.g.
-the contribution of commercial branding to place branding [@Florek2013] or its compliance with the latter [@BassolsiGardella2023] may also be of interest.
+Despite the lack of interest from geographers, the spatial aspects of the activity of law firms worth investigation for a number of reasons.
+Firstly, legal services can be categorised as business or producer services, and this category of services is important for economic development, on both a national and regional scale [@Hansen1993; @Faulconbridge2019].
+Secondly, despite their comparatively minor direct economic impact, they play a significant role as intermediaries and facilitators, contributing to the establishment and maintenance of the rule of law, social order, stability and predictability of social relations.
+Thirdly, for the general public, access to legal aid is vital for the protection of human rights and the attainment of social justice.
+In this regard, the spatial aspects of law services are on a par with the spatial issues of medical care [@Blacksell1988; @Blacksell1990].
 
-There are thousands of law firms in Russia [@Moiseeva2016].
-Their names are likely to reflect some properties of local legal services market.
-The area of Russia is comprised of regions (constituent entities of the federation) that provide some sort of a commonly used spatial unit for geographical studies.
-Besides, economic geographers split the country into 11 economic regions [@Leyzerovich2010].
-Each economic regions includes several constituent entities and is characterized by internal integrity, economic links between the companies, specialization and difference from the others.
-It can be hypothesized that the proximity of regions, as well as internal unity and economic links within the economic regions, leads to the similarity of law firms activity and, correspondingly, to the similarity of their naming.
-The overall aim of this study is to check whether this is true.
-To achieve this goal, a few research questions are asked and then answered based on the data on law firms names.
-These questions, or problems, are specified below.
+The study of firm names — which are sometimes also referred to as company names, brand names or simply “brands” — is a relatively uncommon yet potentially fruitful approach to the geographical analysis of services and related problems.
+A firm name is designed to distinguish the business from competitors, to highlight the sector or geographical area in which it operates, to convey information about the services offered by a provider and the associated benefits.
+A brand is therefore capable of transferring a substantial amount of information in a brief textual format.
+Such information may prove useful in uncovering the city's business landscape and consumer perceptions of a particular city with its distinctive services [@Raento2001].
+It may also help to analyze trends common to a specific sector in a geographic region [@Marjavaara2022].
+The incorporation of place names (toponyms) in brands influences the business development and consumer attitudes [@Peluso2012; @Zhang2014; @Erdogan2016; @Noorda2019].
+Company names encapsulate a multitude of intertwined properties relevant to the economy and culture of a given location.
+This synthesis makes them suitable for the identification of regions, especially in the case of vernacular regions [@Reed1976; @Liesch2015; @Vukosav2016; @Holtkamp2018].
 
-Question 1 (Q1) is whether the neighboring regions have more similar law firm names that regions that do not share a common border.
-Question 2 (Q2) is a continuous extension of Q1: whether the geographical proximity of regions has an impact on the similarity of law firm names, i.e.
-whether the regions that are close to each other have more similar names, and vice versa.
-Question 3 (Q3) moves up from the level of regions to the level of economic regions: whether names within the economic region are more similar compared to the names outside the region.
-Question 4 (Q4) is what naming strategies exist in Russia and how they are spatially organized.
-Question 5 (Q5) is a follow-up from the previous: are there strategies common or different within each economic region?
+It seems reasonable to posit that the names of Russian law firms reflect some economic and, to a lesser extent, cultural characteristics of the places where these firms are located.
+The substantial number of such firms (tens of thousands according to @Moiseeva201) appears to be sufficient for a comprehensive and nuanced representation of areas and territories.
+It can be hypothesized that there is a geographical variation in the naming of law firms across the country, which is contingent upon a number of factors.
+The geographical proximity and common borders, for example, should lead to more homogeneous naming practices.
+Similarly, economic links between places and territories are also expected to reduce the diversity of law firm names.
+In addition, it may be hypothesized that there are several law firm naming strategies, or typical models of brand construction, that potentially vary across the country.
+The primary aim of this study is to test these hypotheses.
 

### 2024-07-27 law-firms-names/Paper.Rmd
Edit part about data, #5

@@
 
-The issue of obtaining information about firm names is challenging.
-Even though all Russian organisations are registered in the unified state registry operated by Federal Tax Service (FTS of Russia), and an extract about a particular company from this registry can be downloaded online by any person free of charge, there is no straightforward way to get names of all companies from the registry at once without paying a considerable amount of money and without negotiating a contract with the responsible government body.
-There are a few commercial firms that re-cell the data from the registry of companies, but the prices are substantial.
-To overcome these problems, a Unified state registry of small and medium-sized businesses (SMB registry) was used.
-This registry has been maintained since 2016 according to the Article 4.1 of Federal Law of July 24, 2007 No 209-FZ “On the development of small and medium-sized businesses in the Russian Federation”.
-All the companies and individual entrepreneurs that have a yearly revenue below 2 billion roubles and an average yearly number of employees below 250 are automatically included in the SMB registry without any action required on their side.
-In contrast to the main registries of companies and entrepreneurs, SMB registry can be fully downloaded at the FTS open data portal free of charge, as well as the monthly history of its updates since the beginning of the operation.
-Thus, this registry can be treated as the most comprehensive free data source with the information about Russian business entities (organisations and individuals).
-The downloadable version of the registry includes, in particular, firm names, addresses of registration (up to a settlement), and codes of activity kinds according to the All-Russia Classifier of Kinds of Economic Activity.
-Large firms are not present in the registry, so some data is missing.
-However, the majority of commercial law firms in Russia (more than 75%) can be categorized as small and medium-sized businesses and are included in the registry, so the availability of information is relatively high, and it can be used for trustworthy conclusions.
+The issue of obtaining information about firm names is a challenging one.
+All Russian organisations are registered in the state registry operated by the Federal Tax Service (FTS of Russia).
+An extract from this registry about a particular company can be searched and downloaded online by any person free of charge.
+However, a considerable sum of money must be paid and a written request submitted to the FTS of Russia to purchase a complete copy of the registry.
+Commercial companies offer data re-cell services, but the prices are similarly high.
+
+To address these challenges, a unified state registry of small and medium-sized businesses (SMB registry) was used.
+The registry has been maintained since 2016 in accordance with the Article 4.1 of the Federal Law of 24 July 2007 No.
+209-FZ, entitled “On the development of small and medium-sized businesses in the Russian Federation”.
+All companies and individual entrepreneurs with a yearly revenue below 2 billion roubles and an average yearly number of employees below 250 are automatically included in the SMB registry, without any action being required on their part.
+The registry is fully downloadable at the FTS open data portal at no cost.
+Additionally, the portal provides a monthly record of updates made since the registry's inception.
+To sum it up, the SMB registry can be regarded as the most comprehensive free data source, offering information on Russian business entities, both organisations and individuals.
+
+The downloadable version of the registry includes, in particular, firm names, addresses of registration (up to a settlement), and codes of activity kinds according to the National Classification of Economic Activities (NCAE).
+It should be noted that the registry does not include large firms, resulting in some data being absent.
+Nevertheless, the majority of commercial law firms in Russia (in excess of 75%) are classified as small and medium-sized businesses and thus are included in the registry.
+Consequently, the availability of information is relatively high, and it can be used to draw reliable conclusions.
 

### 2024-07-29 law-firms-names/Paper.Rmd
Edit methods: law firms definition, period of analysis, SMB data preprocessing, firm names embeddings, #5

@@
 
-The downloadable version of the registry includes, in particular, firm names, addresses of registration (up to a settlement), and codes of activity kinds according to the National Classification of Economic Activities (NCAE).
+The downloadable version of the registry includes, in particular, firm names, addresses of registration (up to a settlement), and codes of activity kinds according to the National Classification of Economic Activities (NCEA).
 It should be noted that the registry does not include large firms, resulting in some data being absent.
@@
 
-### 2.2.1. FTS data processing
+### 2.2.1. Law firms selection criteria
 
-SMB registry dumps from FTS website have a large volume (≈200 Gb in total) and a complex structure: each dump is an archive of several thousand XML files, and each XML file contain 900 records with various information about organisations and individuals.
-Dumps are monthly, resulting in ≈90 archives for the period from 2016 to the present.
-If unpacked, all archives would occupy more than 2 Tb of disk space, and the extraction and preprocessing of such volume of data would take a large time.
-It should be noted, though, that the majority of information is redundant for the task in hand, because it is duplicated due to data publication specific (each archive contains a full copy of the registry, and if nothing has changed during the month, the data records will be merely the same) and because only the data about law firms is required, while the registry holds information about all the other firms as well.
-To extract necessary data from the raw archives, an open-source Python command-line tool was developed named ru-smb-companies.
-The main stages of data extractions are outlined in the next paragraph, while for the complete information about data processing workflow readers may refer to the source code of the program.
+In this study, the term “law firm” is defined as a commercial organisation registered in Russia in accordance with the Civil Code of Russia, with a main activity code equal to 69.10 (activity in the area of law) according to NCEA.
+The aforementioned definition excludes individual entrepreneurs, foreign companies, non-profit organisations, advocacy firms, and notaries.
+The selection technique based on the main activity code was derived from that proposed by @Moiseeva2016.
+Individual entrepreneurs were excluded from the analysis, because they typically operate under their personal names, and even if they have a brand, it is not listed in the SMB registry.
+Other types of firms were not included in the analysis primarily due to data availability issues.
 
-FTS data processing took several steps.
-First, all source archives available at the time of research (November 2023) were downloaded  from FTS servers and stored both locally and in the cloud.
-Next, information about law firms was extracted from each archive to a CSV file.
-Extracted attributes include company or person name, address of incorporation (region, district, city, settlement), taxpayer ID, main activity code and some other properties.
-After this, CSV tables were combined into one table, deduplicated, and raw addresses were normalized and geocoded to fix the inconsistency in location names and add geographical coordinates.
-Finally, the resulting table was transformed in a panel view so that each row represents one business entity at a given year.
-The output table contains data about ≈ 30, 000 law firms for 2016–23.
+The analysis covers a period of six years, from 2016 to 2021.
+The initial point in time is defined by the commencement of SMB registry data availability.
+Although data for 2022 and subsequent years are available, they have not been studied as the ongoing war may have had a significant impact on both the economy and the dissemination of information by government bodies.
+The purpose of this research is to provide conclusions about the space and names under “normal” conditions, and it would therefore be unwise to consider data collected during the period when the circumstances are away from normal.
+Organisations with a lifespan of less than three years have been omitted from the research, which are likely to be dummy companies.
 
-### 2.2.2. Firm names processing
+### 2.2.2. Firm data acquisition
 
-A major challenge regarding the methods of this study is the working with names.
-The objectives of the research imply that names should be grouped and compared in some way.
-This can easily be accomplished with numbers, but firm names are just short text sequences.
-Of course, a human can easily say whether two names are similar or not and classify them.
-However, the human-based approach does not scale well, and the quantity of names requires automation.
-There are several traditional techniques allowing us to compare text strings.
-For example, edit distance calculates the number of atomic changed required to turn one string to another, and the edit distance between “cat” and “car” is 1, while the edit distance between “car” and “karst” is 3.
-Another method named n-gram similarity splits the strings into subsequences, or tokens, and finds the number of common tokens, so that “law company” and “law bureau” are more close to each other than “law bureau” and “juridical center”.
-Despite their simplicity, they also have a significant disadvantage: they cannot account for the intrinsic variability and flexibility of language and do not consider the meaning of the words and phrases rather than their formal representation.
-For instance, a human understands that “law company” and “legal organisation” mean almost the same, while edit distance between these strings is high, and n-gram similarity is low.
-A modern method called text embeddings (sometimes referred to as vectors) can deal with this issue and therefore it is used for this research.
+The processing of SMB registry data was conducted in a series of stages.
+In the initial phase of the research process, all source archives were downloaded.
+Each source archive contained a full copy of the registry data for the specified publication date, with a new archive becoming available on a monthly basis.
+Subsequently, data pertaining to law firms was extracted from the archives and stored in CSV files.
+Each CSV file contained data from one source archive.
+Subsequently, all CSV files were consolidated into a single table, the duplicated records were removed, and the remaining records were augmented with start and end temporal markers.
+Subsequently, the addresses were normalised to resolve the inconsistencies in location names and geocoded to add geographical coordinates.
+Finally, the resulting table was transformed into a panel view, with each row representing a single law firm at a given year.
+All these stages were implemented in an open-source Python command-line tool.
 
-Text embedding, or vector, is a numeric representation of a word, sentence or a document usually designed to catch the meaning of the text.
-An embedding typically looks like just a sequence of decimals with fixed length, i.e.
-the count of elements in this sequence does not depend on the length of the input text, so that a short sentence or an entire paragraph are represented as a sequence of, say, 256 numbers.
-Vectors allow simple computations to find out whether they are more or less similar to each other, and the similarity of vectors corresponds to the similarity of texts.
-Thus, by computing a mathematical distance between embeddings, one can conclude about the semantic distance between texts.
-This is right the case of firm names comparison, similarity, and grouping.
+### 2.2.3. Firm names embeddings retrieval
 
-There are various methods of obtaining embeddings for different texts, e.g.
-Word2Vec, GloVe, FastText.
-The newest GPT-based pretrained large language models such as ChatGPT are also capable of producing text vectors.
-For this study, embeddings from YandexGPT model were used.
-These embeddings were obtained for each unique firm name via public API of the model.
-The vector dimensionality is 256, i.e.
-each vector is a sequence of 256 numbers.
-All the concrete hypothesis testing techniques outlined in the next subsection are based on the use of these vectors.
+The Yandex Foundation Models cloud service was used to transform the firm names into text vectors, or embeddings.
+The “text-search-query” model was selected because its purpose, as stated in the documentation, is to vectorise short texts.
+Prior to vectorisation, the firm names were preprocessed to remove indications of organisational form such as “limited liability company”.
+This was done because such indications are common to the majority of names and thus have little value.
+The results of the queries to the models API were stored separately for reuse, given that API calls are paid and take a time to be completed.
 
@@
 Also, in general it is expected that there are several clear and meaningful firm naming groups, or naming strategies, and that these groups may have (or not) some clear geographical patterns.
-
-### 2.2.4. Other important considerations
-
-The time range of the source data is from 2016 to 2023.
-Only the firms that have existed for at least 3 years are included in the analysis.
-Only organizations are studied, while individual entrepreneurs are omitted, because they do not have firm names.
-Firm names are preprocessed to remove any parts pointing to the legal form of the business (e.g.
-limited liability company or public stock company), because these parts are common to the majority of names and thus do not add anything valuable.
-Law firms are selected by filtering using the following condition: main activity code equals 69.10 (activity in the area of law according to All-Russia Classifier of Kinds of Economic Activity).
-This filtering technique is derived from @Moiseeva2016.
 

### 2024-07-29 law-firms-names/Paper.Rmd
Add subsection about region embeddings to methods, #5

@@
 It seems reasonable to posit that the names of Russian law firms reflect some economic and, to a lesser extent, cultural characteristics of the places where these firms are located.
-The substantial number of such firms (tens of thousands according to @Moiseeva201) appears to be sufficient for a comprehensive and nuanced representation of areas and territories.
+The substantial number of such firms (tens of thousands according to @Moiseeva2016) appears to be sufficient for a comprehensive and nuanced representation of areas and territories.
 It can be hypothesized that there is a geographical variation in the naming of law firms across the country, which is contingent upon a number of factors.
@@
 The results of the queries to the models API were stored separately for reuse, given that API calls are paid and take a time to be completed.
+
+### 2.2.4. Region embeddings
+
+The embeddings of firm names were grouped by regions and averaged.
+In this paper, these average vectors are referred to as region embeddings, or region vectors.
+Russia is comprised of 83 internationally recognised regions (constituent entities of the Russian Federation), hence 83 region vectors were calculated.
+Each vector represents the combined meaning associated with the names of law firm names within a specific region.
+The mathematical similarity of region vectors is analogous to the similarity of law firm names in regions.
+
+Regions vectors were introduced in this study to reduce computational complexity.
+With thousands of law firms, the mathematical operations between individual names would otherwise have been unduly time-consuming.
+Furthermore, the combined vectors improve interpretation of the results.
+A region is a prevalent subdivision used in the studies of Russian economic geography.
+Therefore, a single sequence of numbers for a single region is more readily understandable than a big table of individual name vectors.
 

### 2024-07-30 law-firms-names/Paper.Rmd
Add a subsection about naming strategies identification to methods, #5

@@
 
+### 2.2.5. Naming strategies identification
+
+Law firm names were clustered using the KMeans technique.
+A matrix of features for clustering was constructed from the name embeddings.
+As there were 256 items in each vector, the feature matrix had 256 columns.
+Target number of clusters was determined with elbow method and was ultimately set to 50, with the understanding that further manual processing of the clusterisation results would be necessary.
+Each name was assigned a cluster label between 1 and 50.
+
+The resulting clusters were subsequently subjected to manual grouping.
+A random sample of 20 names was selected from each cluster.
+With 50 clusters and 20 sampled names allocated in each, the total size of the dataset for manual processing is 1, 000.
+The cluster samples were carefully examined, and a concise description was provided for each, e.g.
+“Names with the word “консалт/консалтинг” (consult/consulting)”.
+After this, the clusters were examined once more and assigned to one or more of the four groups: “Form”, “Law”, “Service”, “Misc”.
+The mapping of clusters and groups (e.g.
+cluster 1 — “Law”) was employed to link all the firm names to the appropriate groups.
+The concept of naming strategies was derived from the works of @Arora2015 and @BassolsiGardella2023.
+However, the specific groups differed from those used in their respective papers and were drawn from the data-driven analysis.
+
+Each group except for the “Misc” category represents a specific naming strategy.
+The “Form” strategy encompasses names that are based on a word or words denoting a kind of business entity, including “company”, “firm”, “group”, “partnership”, “center”, “alliance”, and “corporation”.
+The “Law” strategy emphasises the firm's affiliation with the legal services market, employing terms such as “legal”, “juridical”, “lex”, “law”, “lawyer”.
+Names belonging to the “Service” strategy may indicate a particular service provided by a law firm (“advisor”, “consulting”, “protection”, “support”, “warrant”), describe the sectors of businesses the firm is primarily engaged with (“technology”, “development”, “house management”, “accounting”), or mention services in general.
+The “Misc” category is a catch-all group for names that do not clearly align with any other category.
+
 ### 2.2.3. Hypothesis testing

### 2024-07-30 law-firms-names/Paper.Rmd
Edit subsections about hypotheses testing, #5

@@
 
-### 2.2.3. Hypothesis testing
+### 2.2.6. Analysis of firm names similarity
 
-To answer Q1, firm names vectors by each region were averaged so that all names of a region are represented with a single vector that equals to the mathematical mean of all firm names vectors within this region.
-All regions are divided into two groups depending on the presence of common border between them.
-Pairwise distances between all the regions are calculated, and then median distance between regions in each of two groups is calculated.
-The results are additionally visualized as a box plot.
-It is expected that median distance between neighboring regions is smaller than median distance between regions that do not have a same border.
+The similarity of law firm names between regions was calculated as a euclidean distance between the corresponding region vectors.
+Henceforth, this will be referred to as a semantic distance between regions.
+A neighborhood of regions was determined on the basis of the existence of a common border between them, thus allowing for two regions to either be neighboring or not.
+A geographic distance between regions was calculated as a linear distance between the centroids of the region polygons.
+To provide a proxy of economic links between regions, the belonging to the same economic region was utilized.
+According to @Leyzerovich2010, Russia is comprised of 11 economic regions, which themselves consist of a number of regions.
+The defining characteristics of an economic region are its internal unity, distinction from the other economic regions, and the economic links that exits between constituting regions, cities and enterprises within them.
 
-The similar technique is used for Q2.
-Again, the mean vector of all firm names for each region is computed, and pairwise semantic distance between regions is calculated.
-Then, a geographical distance between the centroids of regions is also measured.
-A correlation between geographical distance and semantic distance is computed, and the result is plotted.
-It is expected that the coefficient of correlation is positive.
+To estimate the effect of neighboring, regions were divided into pairs of neighbors and non-neighbors.
+Semantic distances were then calculated between the regions in each pair within the two groups.
+A median distance was calculated for each group.
+It was expected that the median semantic distance between neighboring regions would be less than that between regions that do not share a border.
 
-Q3 also builds upon the pairwise semantic distances between regions.
-After these distances are found out, regions are grouped by economic regions.
-For each economic region, two metrics are calculated: the first is a median distance between regions within this econoimic region, and the second is a median distance between regions within and without this economic region.
-It is expected that within-median-distance is smaller that beyond-median-distance.
-The results are additionally illustrated on a boxplot.
+A similar technique is used to ascertain whether geographical distance impacts semantic distance.
+Pairwise semantic and geographical distances between all regions were calculated, and the correlation between geographical distance and semantic distance was estimated.
+It was expected that the coefficient of correlation would be positive.
 
-Q4 and Q5 follow a slightly different methodics.
-First, all firm names are clustered with KMeans algorithm (number of clusters is 50).
-After clustering, a random sample of names from each cluster is taken, and these names are manually checked, described and tagged with the labels of more broad groups.
-Then these manually defined groups are assigned to names using clusters as links between groups and individual names.
-The number of names belonging to each group in each region is calculated, and the results of this calculation are mapped on a tile-grid map of Russia to analyze the spatial properties of grouping.
-In this way, Q4 is processed.
-For Q5, the regions are marked with the label of the most popular group, and the number of regions with different groups within an economic region is counted.
-It is expected that each economic regions is characterized with only one majority group.
-It may be the same as the group for another economic region, but a small if any variation is expected within an economic region to prove its integrity.
-Also, in general it is expected that there are several clear and meaningful firm naming groups, or naming strategies, and that these groups may have (or not) some clear geographical patterns.
+To analyse the role of economic links, the pairwise semantic distances between regions were split into two groups: distances between regions within an economic region (within-distances) and distances between regions belonging to an economic region and all the other regions (outside-distances).
+The median of both within-distances and outside-distances was calculated for each economic region.
+It was expected that semantic distances between regions within an economic region would be smaller than those between regions belonging to different economic regions.
+
+### 2.2.7. Analysis of naming strategies
+
+A dominant naming strategy is ascribed to each region, defined as the naming strategy used by the majority number of law firms within that region.
+Dominant naming strategies are then mapped and analysed visually to ascertain whether any geographical patterns emerge.
+In addition, the boundaries of economic regions are illustrated on the same map, and the dominant naming strategies of regions within each economic region are examined.
+No a priori hypotheses are formulated regarding the geographical patterns.
+As for naming strategies within economic regions, it is expected that they will be similar.
 

### 2024-07-31 law-firms-names/Paper.Rmd
Edit results and discussion, #5

@@
 
-## 3.1. Semantic distance between heighboring regions is smaller
+## 3.1. Law firm names in neighboring regions are more similar
 
-Figure 1 shows the median semantic distance between law firm names of neighboring regions versus the same of regions that do not have a common border.
-Despite the difference in medians is relatively small, it does exist, and the overall distribution of values for non-neighboring regions is shifted to the area of higher distances compared to the distribution of values for bordering regions.
-Thus, the hypothesis from Q1 turns out to be true: neighboring regions are indeed closer to each other in terms of semantic distances between their law firm names.
+The semantic distance between neighboring regions in comparison to the semantic distance between regions that do not have a common border is illustrated in Figure 1.
+Although the difference in medians is relatively minor, it is nevertheless present, and the overall distribution of distances between non-neighboring regions is shifted towards the area of higher values.
+Therefore, neighboring regions have more similar names of law firms than regions that do not border one another.
 
-```{r fig-1-neighbors, fig.cap="Figure 1. The relationship between neightboring status of regions and semantic distance between names of law firms incorporated in these regions", fig.height=3}
+```{r fig-1-neighbors, fig.cap="Figure 1. Semantic distances between neighboring and non-neighboring regions", fig.height=3}
 neighbor_plot
@@
 
-## 3.2. The larger the geographical distance, the larger is semantic distance
+## 3.2. Greater geographical distance reduces the similarity of law firm names
 
-Figure 2 shows the continuous analog of Figure 1, i.e.
-the scatter plot of geographical versus semantic distance between regions according to their law firms names.
-The observed correlation is weak yet positive.
-Besides, there are two clusters of points.
-Thus, for Q2 the answer is partial: there is a positive relationship between the geographical distance and semantic distance of law firm names between regions, but the observed correlation is weak, and also there is a minor group of region pairs that seems to have no such correlation at all.
+The relationship between geographical and semantic distances is shown in Figure 2.
+The correlation coefficient is relatively low but positive.
+Thus, regions that are situated close to each other tend to have a bit more similar names of law firms even in the absence of a common border between them.
 
-```{r fig-2-distance-plot, fig.cap="Figure 2. Relationship between geographical distance between regions and semantic distance between names of law firms incorporated in these regions", fig.height=3}
+```{r fig-2-distance-plot, fig.cap="Figure 2. Relationship between geographical and semantic distances between regions", fig.height=3}
 distance_plot
@@
 
-## 3.3. Semantic distance within economic regions is smaller
+## 3.3. Law firm names inside an economic region are more homogeneous
 
-Figure 3 shows the comparison of distances between law firm names within economic regions and outside them.
-The results are mixed.
-In some cases, the distance between regions belonging to the same economic region is a bit smaller than the distance between regions belonging to an economic region and other regions that do not belong to this economic region.
-However, there are several economic regions where this tendency does not holds.
-In addition, it looks like that the overall shape of semantic distance distributions in these economic regions imply that there are internal subdivisions within this economic region, and thus it seems to be not as united and integral as it is theoretically suggested.
-This observation has a potential to be quite intriguing for checking the validity of economic regions classification in Russia.
-Nevertheless, its relative importance in the context of regioning task is quite low, and thus there is no need to make provisions on classification updates right now.
+Within-distances and outside-distances by economic regions, as outlined in the methods section, are depicted in Figure 3.
+In some instances, the semantic distance between regions that are part of the same economic region is slightly less than the semantic distance between these regions and regions of other economic regions.
+However, this pattern does not apply to at least three economic regions: in Volga, North, and North Caucasus, within-distance is equal to or greater than outside-distance.
+Consequently, the results of this test are mixed: while links between regions constituting an economic region usually slightly increase the similarity of law firm names, there are several exceptions to this rule.
+A greater within-distance compared to outside-distance may indicate internal heterogeneity within an economic region, thereby suggesting the need for a classification update.
 
@@
 
-## 3.4. There are three primary naming strategies: form-, field-, service-based
+## 3.4. Geographical patterns of naming strategies are unclear
 
-Manual analysis of clustered names samples shows that all the law firm names, except for uncategorized, can be grouped into three generic catgories: form-based, field-based, service-based names.
-*Form-based names* are focused on the organizational form, or type, of business, company or firm and usually include the words like “company”, “partnership”, “corporation”, “alliance”, “center”, “bureau”.
-In contrast, *field-based names* point to the field of company's activity, i.e.
-law, and thus are usually based on law-related words such as “legal”, “juridical”, “lex”.
-*Service-based names* mention the service nature of the business in general by using words “services” or address the specific kinds of services or areas of related business, e.g.
-“consulting”, “analytics”, “expertise”, “bankruptcy”, “arbitrazh”, “accounting”, “finance”, “real estate”.
-As seen in Figure 4, field-based and service-based naming strategies dominate over form-based, sharing in total more than 80% of all strategical law firm names in the majority of regions.
-Consequently, all the regions may be divided into two broad groups: either with field-based naming of law firms or with service-based naming of law firms.
-The spatial patterns of these grouping are nevertheless obscure, with no clear geographical tendencies, and the overall spatial distribution of these naming strategies looks random, except for the prevalence of service-based names in the European South.
+Map in Figure 4 depicts a dominant naming strategy in regions of Russia.
+As “Form” naming is used by a minority of law firms across all regions, it is not shown.
+European South of Russia and Volga economic region are characterized by a prevalence of “Service” strategy.
+In other parts of the country, an irregular mixture of both “Law” and “Service” naming strategies is observed.
 
-```{r fig-4-naming-strategies, fig.cap="Figure 4. Map of naming strategies by regions and economic regions"}
+```{r fig-4-naming-strategies, fig.cap="Figure 4. Map of naming strategies"}
 naming_strategies
@@
 
-## 3.5. Naming strategies are not consistent over economic regions
+## 3.5. Naming strategies within economic regions are inconsistent
 
-From Figure 4 one can easily conclude that few economic regions are characterized by a consistent naming strategy.
-In Volga-Vyatka region, law-based strategy is the most popular one among all the regions, except for the Republic of Mari El.
-In Volga and North Caucasus, service-based strategy prevails in the majority of regions.
-The same also holds for the Eastern Siberia, though the large size of the Krasnoyarsk territory, the only exception, overweights the quantity of regions with service-based stratery, thus the economic region in general can not be treated the same as Volga and North Caucasus.
-All the other economic regions are characterized by a blend of law firms naming strategies.
+As seen from Figure 4, few economic regions are characterized by a uniform naming strategy.
+In Volga-Vyatka economic region, “Law” strategy is the most prevalent among all the regions, with the exception of the Republic of Mari El.
+In Volga and North Caucasus economic regions, service-based strategy is the prevailing approach in the majority of regions.
+The remaining economic regions exhibit a combination of law firms naming strategies.
 

### 2024-07-31 law-firms-names/Paper.Rmd
Edit conclusion, #5

@@
 
-The results of the research are mixed.
-On the other hand, several hypothesis have been proven: law firm names in neighboring regions are more similar than law firm names in non-neighboring regions; the smaller the geographic distance between regions, the more similar the law firm names; law firm names within an economic region are typically more similar compared to the law firm names outside an economic regions.
-On the other hand, the difference in the metrics of similarity is relatively small in all these cases, as well as the correlation coefficient, thus it should be noted that although the hypothesized phenomena do exist, their magnitude is weak.
+The findings of the study are somewhat contradictory.
+On the other hand, several hypotheses have been proven.
+These include the following: law firm names in neighboring regions are more similar than law firm names in non-neighboring regions; the smaller the geographic distance between regions, the more similar the law firm names; and law firm names within an economic region are typically more similar compared to the law firm names outside an economic region.
+On the other hand, the difference in the metrics of similarity is relatively small in each case, as is the correlation coefficient.
+It is therefore important to note that although the postulated phenomena do indeed exist, their magnitude is weak.
 
-There are three primary law firm naming strategies: form-based, law-based, service-based.
-The form-based strategy is in a minority, accounting for ≈10% of all the names.
-Two other strategies share the remaining majority, and in some regions, law-based naming prevails, while in the others, service-based naming is more common.
-Service-based law firms naming is a dominant strategy in the majority of regions in the European South of Russia.
-Other geographical regularities regarding the law firm naming are unclear.
-Economic regions are typically characterized by a mixture of naming strategies, expect for Volga-Vyatka with dominating law-based strategy, and Volga with North Caucasus with service-based strategy prevailing in the majority of constituting regions.
+The three principal strategies for naming law firms are as follows: “Form”, “Law”, and “Service”.
+The first of these represents a minority approach, while the remaining majority is divided between two other strategies.
+In the European South of Russia and in Volga economic region, “Service” is a dominant strategy.
+However, no other spatial patterns in law firms naming have been identified.
+Economic regions are typically characterized by a mixture of naming strategies, expect for Volga-Vyatka, where “Law” strategy prevails, and Volga and North Caucasus, where “Service” strategy is dominant.
 
-The contribution of this study is mostly theoretical and methodological.
-It emphasizes the importance of firm names as the source of information for business- and economy-related research.
-It also proposes a technique of using modern natural language processing (NLP) solutions based on artificial neural networks for integral analysis of company naming in a geographical context, as well as the usage of disaggregated administrative open data for a spatial analysis.
-The results argue for the effect of geographical proximity and neighboring on the similarity of economical and (to some extent) cultural properties of the territories.
-They also generally support the widely used classification of economic regions in Russia, though noticing a few weak places where there is an internal heterogenity within an economic region.
-The study also offers an example of semi-automated company names classification in a particular field of economic activity and points at some kind of geographical differentiation in the naming strategies, that may be subject to further spatial analysis.
+The contribution of this study is primarily theoretical and methodological in nature.
+It underscores the significance of firm names as a source of information for business- and economy-related research.
+It also proposes a technique for comprehensive analysis of branding in a geographical context through the use of modern natural language processing (NLP) solutions based on artificial neural networks.
+Additionally, it advocates for the utilization of disaggregated administrative open data for a spatial analysis.
+The findings demonstrate the effect of geographical proximity, neighboring, and economic relations on the similarity of the economic and, to a certain extent, cultural properties of the territories represented in firm names.
+The results generally align with the widely accepted classification of economic regions in Russia, although they highlight a few instances where a theoretically undesired internal heterogeneity within an economic region is evident.
+Finally, the study provides an illustration of a semi-automated brand classification within a specific economic sector and discovers a geographical variation in naming strategies that could be further investigated.
 

### 2024-07-31 law-firms-names/Paper.Rmd
Edit abstract, #5

@@
 
-**Abstract:** the research is focused on integral analysis of law firm names in Russia and its geographical aspects.
-The main problem of the study is to find out whether several spatial relations between subdivisions of the country, namely neighboring, proximity, and belonging to an economic region, are reflected in law firm naming, and how law firm naming depends on these relations.
-To conduct the analysis, data about law firm names is extracted from the open dumps of the state small and medium-sized businesses registry.
-Law firm names are converted into numeric vectors using YandexGPT embeddings, then clustered with KMeans method, and manually grouped to detect main naming strategies.
-Numeric representations of law firm names within each country's subdivision are averaged to get a regional embedding, and then law firm names of the regions are compared using regional embeddings.
-It is found out that regions that are geographically closer to each other or have a common border tend to have slightly more similar law firm names.
-In addition, regions belonging to the same economic region have more similar law firm names either.
-There are three main law firms naming strategies: form-based, law-based, service-based.
-Volga and North Caucasus economic regions are characterized by the prevalence of service-based strategy, and Volga-Vyatka economic region has a law-based strategy, while other territories have mixed naming strategies.
-The results of the study support the existing widely used classification of economic regions in Russia and argue the impact of neighboring, proximity, and links on the economic and cultural properties of the territories.
-The administrative open data processing techniques, as well as methods of working with firm names based on neural networks proposed in this paper may be used by other economic geographers for their research purposes.
+**Abstract:** the present study is an analysis of law firm naming in Russia, with a particular focus on the geographical aspects of this phenomenon.
+The primary objective of this research is to ascertain the impact of the spatial relations between the regions of the country, specifically those of a neighboring, proximity, and belonging to a parent-level subdivision, on the naming of law firms.
+To conduct the analysis, data regarding law firms is extracted from the open dumps of the state registry of small and medium-sized businesses.
+The names of the firms are transformed into numerical vectors, subsequently clustered with KMeans method, and then manually grouped to identify naming strategies.
+Numerical representations of law firm names within each region are averaged to get region embeddings, which are then used to compare the names of law firms in different regions.
+The research findings indicate that regions situated in closer proximity to one another or sharing a common border tend to adopt slightly more similar law firm names.
+Furthermore, regions that are part of the same economic region also display a greater degree of similarity in law firm names.
+Three primary strategies of law firm naming are “Form”, “Law“, and “Service”.
+Volga and North Caucasus economic regions are characterized by the predominance of “Service” strategy, whereas Volga-Vyatka economic region exhibits a “Law” strategy, and the remaining territories demonstrate a combination of naming strategies.
+The results of the study lend support to the widely-used classification of economic regions in Russia.
+The findings also underscore the impact of neighboring, proximity, and interconnectivity on the economic and cultural attributes of the regions.
+The administrative open data processing techniques, as well as the methods of working with firm names based on neural networks proposed in this paper, may be used by other economic geographers for their own research purposes.
 

### 2024-08-08 law-firms-names/Paper.Rmd
Various minor improvements in paper text, code,  style, and refs, #5

@@
 ---
-title: "Spatial Analysis of Russian Law Firm Names"
+title: "Spatial Analysis of Russian Law Firms Naming"
 author: "Pavel Syomin¹"
@@
   fig.id = FALSE,
-  dpi = 300)
+  dpi = 1200)
+IS_PAPER <- TRUE # used in script to disable saving of names and samples
 ```
@@
 
-**Abstract:** the present study is an analysis of law firm naming in Russia, with a particular focus on the geographical aspects of this phenomenon.
-The primary objective of this research is to ascertain the impact of the spatial relations between the regions of the country, specifically those of a neighboring, proximity, and belonging to a parent-level subdivision, on the naming of law firms.
+**Abstract:** The present study analyzes law firm naming in Russia, with a particular focus on the geographical aspects of this phenomenon.
+The primary objective of this research is to ascertain the impact of the spatial relations between the country's regions, specifically those of a neighboring, proximity, and belonging to a parent-level subdivision, on the naming of law firms.
 To conduct the analysis, data regarding law firms is extracted from the open dumps of the state registry of small and medium-sized businesses.
-The names of the firms are transformed into numerical vectors, subsequently clustered with KMeans method, and then manually grouped to identify naming strategies.
+The names of the firms are transformed into numerical vectors, subsequently clustered with the KMeans method, and then manually grouped to identify naming strategies.
 Numerical representations of law firm names within each region are averaged to get region embeddings, which are then used to compare the names of law firms in different regions.
-The research findings indicate that regions situated in closer proximity to one another or sharing a common border tend to adopt slightly more similar law firm names.
-Furthermore, regions that are part of the same economic region also display a greater degree of similarity in law firm names.
+The research findings indicate that regions situated closer to one another or sharing a common border tend to adopt slightly more similar law firm names.
+Furthermore, regions that are part of the same economic region also display a greater degree of similarity in law firm naming.
 Three primary strategies of law firm naming are “Form”, “Law“, and “Service”.
-Volga and North Caucasus economic regions are characterized by the predominance of “Service” strategy, whereas Volga-Vyatka economic region exhibits a “Law” strategy, and the remaining territories demonstrate a combination of naming strategies.
-The results of the study lend support to the widely-used classification of economic regions in Russia.
+Volga and North Caucasus economic regions are characterized by the predominance of the “Service” strategy, whereas the Volga-Vyatka economic region exhibits a “Law” strategy, and the remaining territories demonstrate a combination of naming strategies.
+The results of the study lend support to the widely used classification of economic regions in Russia.
 The findings also underscore the impact of neighboring, proximity, and interconnectivity on the economic and cultural attributes of the regions.
@@
 The geography of services has two distinct dimensions: economic and social.
-The former is primarily concerned with the business aspects of the services, while the latter addresses the implications for human well-being arising from the geographical organisation of services [@Tkachenko2016].
+The former is primarily concerned with the business aspects of the services, while the latter addresses the implications for human well-being arising from the geographical organization of services [@Tkachenko2016].
 The existing scientific literature on the geography of services in Russia covers a broad range of topics, including education [@Shulgina2019], car rental [@Zyrianova2018], catering [@Preobrazhenskiy2018], medical care [@Kazantcev2022; @Panin2023; @Nikoloski2024], and internet access [@Nagirnaya2015; @Zemtsov2022].
@@
 
-Despite the lack of interest from geographers, the spatial aspects of the activity of law firms worth investigation for a number of reasons.
-Firstly, legal services can be categorised as business or producer services, and this category of services is important for economic development, on both a national and regional scale [@Hansen1993; @Faulconbridge2019].
-Secondly, despite their comparatively minor direct economic impact, they play a significant role as intermediaries and facilitators, contributing to the establishment and maintenance of the rule of law, social order, stability and predictability of social relations.
+Despite the lack of interest from geographers, the spatial aspects of the activity of law firms are worth investigating for a number of reasons.
+Firstly, legal services can be categorized as business or producer services, and this category of services is important for economic development, on both a national and regional scale [@Hansen1993; @Faulconbridge2019].
+Secondly, despite their comparatively minor direct economic impact, these services play a significant role as intermediaries and facilitators, contributing to the establishment and maintenance of the rule of law, social order, stability, and predictability of social relations.
 Thirdly, for the general public, access to legal aid is vital for the protection of human rights and the attainment of social justice.
-In this regard, the spatial aspects of law services are on a par with the spatial issues of medical care [@Blacksell1988; @Blacksell1990].
+In this regard, the spatial aspects of law services are on par with the spatial issues of medical care [@Blacksell1988; @Blacksell1990].
 
-The study of firm names — which are sometimes also referred to as company names, brand names or simply “brands” — is a relatively uncommon yet potentially fruitful approach to the geographical analysis of services and related problems.
-A firm name is designed to distinguish the business from competitors, to highlight the sector or geographical area in which it operates, to convey information about the services offered by a provider and the associated benefits.
+The study of firm names — which are sometimes also referred to as company names, brand names, or simply “brands” — is a relatively uncommon yet potentially fruitful approach to the geographical analysis of services and related problems.
+A firm name is designed to distinguish the business from competitors, to highlight the sector or geographical area in which it operates, and to convey information about the services offered by a provider and the associated benefits.
 A brand is therefore capable of transferring a substantial amount of information in a brief textual format.
@@
 The issue of obtaining information about firm names is a challenging one.
-All Russian organisations are registered in the state registry operated by the Federal Tax Service (FTS of Russia).
+All Russian organizations are registered in the state registry operated by the Federal Tax Service (FTS of Russia).
 An extract from this registry about a particular company can be searched and downloaded online by any person free of charge.
@@
 
-To address these challenges, a unified state registry of small and medium-sized businesses (SMB registry) was used.
-The registry has been maintained since 2016 in accordance with the Article 4.1 of the Federal Law of 24 July 2007 No.
-209-FZ, entitled “On the development of small and medium-sized businesses in the Russian Federation”.
+To address these challenges, a unified state registry of small and medium-sized businesses (SMB registry) may be used.
+The registry has been maintained since 2016 in accordance with Article 4.1 of the Federal Law of 24 July 2007 No.
+209-FZ “On the development of small and medium-sized businesses in the Russian Federation”.
 All companies and individual entrepreneurs with a yearly revenue below 2 billion roubles and an average yearly number of employees below 250 are automatically included in the SMB registry, without any action being required on their part.
@@
 Additionally, the portal provides a monthly record of updates made since the registry's inception.
-To sum it up, the SMB registry can be regarded as the most comprehensive free data source, offering information on Russian business entities, both organisations and individuals.
+To sum it up, the SMB registry can be regarded as the most comprehensive free data source offering information on Russian business entities, both organizations and individuals.
 
@@
 Nevertheless, the majority of commercial law firms in Russia (in excess of 75%) are classified as small and medium-sized businesses and thus are included in the registry.
-Consequently, the availability of information is relatively high, and it can be used to draw reliable conclusions.
+Consequently, the completeness of information is relatively high, and it can be used to draw reliable conclusions.
 
@@
 
-In this study, the term “law firm” is defined as a commercial organisation registered in Russia in accordance with the Civil Code of Russia, with a main activity code equal to 69.10 (activity in the area of law) according to NCEA.
-The aforementioned definition excludes individual entrepreneurs, foreign companies, non-profit organisations, advocacy firms, and notaries.
-The selection technique based on the main activity code was derived from that proposed by @Moiseeva2016.
-Individual entrepreneurs were excluded from the analysis, because they typically operate under their personal names, and even if they have a brand, it is not listed in the SMB registry.
-Other types of firms were not included in the analysis primarily due to data availability issues.
+In this study, the term “law firm” is defined as a commercial organization registered in Russia in accordance with the Civil Code of Russia, with a main activity code equal to 69.10 (activity in the area of law) according to NCEA.
+The aforementioned definition excludes individual entrepreneurs, foreign companies, non-profit organizations, advocacy firms, and notaries.
+The selection technique based on the main activity code is derived from that proposed by @Moiseeva2016.
+Individual entrepreneurs are excluded from the analysis because they typically operate under their personal names, and even if they have a brand, it is not listed in the SMB registry.
+Other types of law firms are not included in the analysis primarily due to data availability issues.
 
@@
 The purpose of this research is to provide conclusions about the space and names under “normal” conditions, and it would therefore be unwise to consider data collected during the period when the circumstances are away from normal.
-Organisations with a lifespan of less than three years have been omitted from the research, which are likely to be dummy companies.
+Organizations with a lifespan of less than three years have been omitted from the research, which are likely to be dummy companies.
 
@@
 
-The processing of SMB registry data was conducted in a series of stages.
-In the initial phase of the research process, all source archives were downloaded.
-Each source archive contained a full copy of the registry data for the specified publication date, with a new archive becoming available on a monthly basis.
-Subsequently, data pertaining to law firms was extracted from the archives and stored in CSV files.
-Each CSV file contained data from one source archive.
-Subsequently, all CSV files were consolidated into a single table, the duplicated records were removed, and the remaining records were augmented with start and end temporal markers.
-Subsequently, the addresses were normalised to resolve the inconsistencies in location names and geocoded to add geographical coordinates.
-Finally, the resulting table was transformed into a panel view, with each row representing a single law firm at a given year.
-All these stages were implemented in an open-source Python command-line tool.
+The processing of SMB registry data is conducted in a series of stages.
+In the initial phase of the research process, all source archives are downloaded.
+Each source archive contains a full copy of the registry data for the specified publication date, with a new archive becoming available on a monthly basis.
+Subsequently, data pertaining to law firms is extracted from the archives and stored in CSV files.
+Each CSV file contains data from one source archive.
+Subsequently, all CSV files are consolidated into a single table, the duplicated records are removed, and the remaining records are augmented with start and end temporal markers.
+Subsequently, the addresses are normalized to resolve the inconsistencies in location names and geocoded to add geographical coordinates.
+Finally, the resulting table is transformed into a panel view, with each row representing a single law firm at a given year.
+All these stages are implemented in an open-source Python command-line tool.
 
-### 2.2.3. Firm names embeddings retrieval
+### 2.2.3. Firm name embeddings retrieval
 
-The Yandex Foundation Models cloud service was used to transform the firm names into text vectors, or embeddings.
-The “text-search-query” model was selected because its purpose, as stated in the documentation, is to vectorise short texts.
-Prior to vectorisation, the firm names were preprocessed to remove indications of organisational form such as “limited liability company”.
-This was done because such indications are common to the majority of names and thus have little value.
-The results of the queries to the models API were stored separately for reuse, given that API calls are paid and take a time to be completed.
+The Yandex Foundation Models cloud service is used to transform the firm names into text vectors, or embeddings.
+The “text-search-query” model is selected because its purpose, as stated in the documentation, is to vectorize short texts.
+Prior to vectorization, the firm names are preprocessed to remove indications of organizational form such as “limited liability company”.
+This is done because such indications are common to the majority of names and thus have little value.
+The results of the queries to the Yandex API are stored separately for reuse, given that API calls are paid and take time to be completed.
 
@@
 
-The embeddings of firm names were grouped by regions and averaged.
-In this paper, these average vectors are referred to as region embeddings, or region vectors.
-Russia is comprised of 83 internationally recognised regions (constituent entities of the Russian Federation), hence 83 region vectors were calculated.
+The embeddings of firm names are grouped by regions and averaged.
+In this paper, these average vectors are referred to as region embeddings or region vectors.
+Russia is comprised of 83 internationally recognized regions (constituent entities of the Russian Federation), hence 83 region vectors are calculated.
 Each vector represents the combined meaning associated with the names of law firm names within a specific region.
@@
 With thousands of law firms, the mathematical operations between individual names would otherwise have been unduly time-consuming.
-Furthermore, the combined vectors improve interpretation of the results.
+Furthermore, the combined vectors improve the interpretation of the results.
 A region is a prevalent subdivision used in the studies of Russian economic geography.
@@
 
-Law firm names were clustered using the KMeans technique.
-A matrix of features for clustering was constructed from the name embeddings.
-As there were 256 items in each vector, the feature matrix had 256 columns.
-Target number of clusters was determined with elbow method and was ultimately set to 50, with the understanding that further manual processing of the clusterisation results would be necessary.
-Each name was assigned a cluster label between 1 and 50.
+Law firm names are clustered using the KMeans technique.
+A matrix of features for clustering is constructed from the name embeddings.
+As there are 256 items in each vector, the feature matrix has 256 columns.
+A target number of clusters is determined with the elbow method and ultimately set to 50, with the understanding that further manual processing of the clusterization results will be necessary.
+Each name is assigned a cluster label between 1 and 50.
 
-The resulting clusters were subsequently subjected to manual grouping.
-A random sample of 20 names was selected from each cluster.
+The resulting clusters are subsequently subjected to manual grouping.
+A random sample of 20 names is selected from each cluster.
 With 50 clusters and 20 sampled names allocated in each, the total size of the dataset for manual processing is 1, 000.
-The cluster samples were carefully examined, and a concise description was provided for each, e.g.
+The cluster samples are carefully examined, and a concise description is provided for each, e.g.
 “Names with the word “консалт/консалтинг” (consult/consulting)”.
-After this, the clusters were examined once more and assigned to one or more of the four groups: “Form”, “Law”, “Service”, “Misc”.
+After this, the clusters are examined once more and assigned to one or more of the four groups: “Form”, “Law”, “Service”, and “Misc”.
 The mapping of clusters and groups (e.g.
-cluster 1 — “Law”) was employed to link all the firm names to the appropriate groups.
-The concept of naming strategies was derived from the works of @Arora2015 and @BassolsiGardella2023.
-However, the specific groups differed from those used in their respective papers and were drawn from the data-driven analysis.
+cluster 1 — “Law”) is employed to link all the firm names to the appropriate groups.
+The concept of naming strategies is derived from the works of @Arora2015 and @BassolsiGardella2023.
+However, the specific groups differ from those used in their respective papers and are drawn from the data-driven analysis.
 
@@
 The “Form” strategy encompasses names that are based on a word or words denoting a kind of business entity, including “company”, “firm”, “group”, “partnership”, “center”, “alliance”, and “corporation”.
-The “Law” strategy emphasises the firm's affiliation with the legal services market, employing terms such as “legal”, “juridical”, “lex”, “law”, “lawyer”.
+The “Law” strategy emphasizes the firm's affiliation with the legal services market, employing terms such as “legal”, “juridical”, “lex”, “law”, and “lawyer”.
 Names belonging to the “Service” strategy may indicate a particular service provided by a law firm (“advisor”, “consulting”, “protection”, “support”, “warrant”), describe the sectors of businesses the firm is primarily engaged with (“technology”, “development”, “house management”, “accounting”), or mention services in general.
@@
 
-The similarity of law firm names between regions was calculated as a euclidean distance between the corresponding region vectors.
+The similarity of law firm names between regions is calculated as a Euclidean distance between the corresponding region vectors.
 Henceforth, this will be referred to as a semantic distance between regions.
-A neighborhood of regions was determined on the basis of the existence of a common border between them, thus allowing for two regions to either be neighboring or not.
-A geographic distance between regions was calculated as a linear distance between the centroids of the region polygons.
-To provide a proxy of economic links between regions, the belonging to the same economic region was utilized.
+A neighborhood of regions is determined on the basis of the existence of a common border between them, thus allowing for two regions to either be neighboring or not.
+A geographic distance between regions is calculated as a linear distance between the centroids of the region polygons.
+To provide a proxy of economic links between regions, the belonging to the same economic region is utilized.
 According to @Leyzerovich2010, Russia is comprised of 11 economic regions, which themselves consist of a number of regions.
-The defining characteristics of an economic region are its internal unity, distinction from the other economic regions, and the economic links that exits between constituting regions, cities and enterprises within them.
+The defining characteristics of an economic region are its internal unity, distinction from the other economic regions, and the economic links that exist between constituting regions, cities, and enterprises within them.
 
-To estimate the effect of neighboring, regions were divided into pairs of neighbors and non-neighbors.
-Semantic distances were then calculated between the regions in each pair within the two groups.
-A median distance was calculated for each group.
-It was expected that the median semantic distance between neighboring regions would be less than that between regions that do not share a border.
+To estimate the effect of neighboring, regions are divided into pairs of neighbors and non-neighbors.
+Semantic distances are then calculated between the regions in each pair within the two groups.
+A median semantic distance is calculated for each group.
+It is expected that the median semantic distance between neighboring regions would be less than that between regions that do not share a border.
 
 A similar technique is used to ascertain whether geographical distance impacts semantic distance.
-Pairwise semantic and geographical distances between all regions were calculated, and the correlation between geographical distance and semantic distance was estimated.
-It was expected that the coefficient of correlation would be positive.
+Pairwise semantic and geographical distances between all regions are calculated, and the correlation between geographical distance and semantic distance is estimated.
+It is expected that the coefficient of correlation will be positive.
 
-To analyse the role of economic links, the pairwise semantic distances between regions were split into two groups: distances between regions within an economic region (within-distances) and distances between regions belonging to an economic region and all the other regions (outside-distances).
-The median of both within-distances and outside-distances was calculated for each economic region.
-It was expected that semantic distances between regions within an economic region would be smaller than those between regions belonging to different economic regions.
+To analyze the role of economic links, the pairwise semantic distances between regions are split into two groups: distances between regions within an economic region (within-distances) and distances between regions belonging to an economic region and all the other regions (outside-distances).
+The median of both within-distances and outside-distances is calculated for each economic region.
+It is expected that semantic distances between regions within an economic region would be smaller than those between regions belonging to different economic regions.
 
@@
 A dominant naming strategy is ascribed to each region, defined as the naming strategy used by the majority number of law firms within that region.
-Dominant naming strategies are then mapped and analysed visually to ascertain whether any geographical patterns emerge.
+Dominant naming strategies are then mapped and analyzed visually to ascertain whether any geographical patterns emerge.
 In addition, the boundaries of economic regions are illustrated on the same map, and the dominant naming strategies of regions within each economic region are examined.
@@
 
-```{r fig-1-neighbors, fig.cap="Figure 1. Semantic distances between neighboring and non-neighboring regions", fig.height=3}
-neighbor_plot
+```{r fig-1-neighbors, fig.cap="**Figure 1.** Semantic distances between neighboring and non-neighboring regions", fig.height=3}
+neighbors_plot
 ```
@@
 
-```{r fig-2-distance-plot, fig.cap="Figure 2. Relationship between geographical and semantic distances between regions", fig.height=3}
+```{r fig-2-distance-plot, fig.cap="**Figure 2.** Relationship between geographical and semantic distances between regions", fig.height=3}
 distance_plot
@@
 In some instances, the semantic distance between regions that are part of the same economic region is slightly less than the semantic distance between these regions and regions of other economic regions.
-However, this pattern does not apply to at least three economic regions: in Volga, North, and North Caucasus, within-distance is equal to or greater than outside-distance.
+However, this pattern does not apply to at least three economic regions: in Volga, North, and North Caucasus, median within-distance is equal to or greater than median outside-distance.
 Consequently, the results of this test are mixed: while links between regions constituting an economic region usually slightly increase the similarity of law firm names, there are several exceptions to this rule.
@@
 
-```{r fig-3-economic-regions-distance, fig.cap="Figure 3. Semantic distance between regions within and outside economic regions", fig.height=4}
+```{r fig-3-economic-regions-distance, fig.cap="**Figure 3.** Semantic distances between regions within and outside economic regions", fig.height=5}
 economic_regions_distances
@@
 
-Map in Figure 4 depicts a dominant naming strategy in regions of Russia.
+The map in Figure 4 depicts a dominant naming strategy in regions of Russia.
 As “Form” naming is used by a minority of law firms across all regions, it is not shown.
-European South of Russia and Volga economic region are characterized by a prevalence of “Service” strategy.
+European South of Russia and Povolzhye are characterized by a prevalence of the “Service” strategy.
 In other parts of the country, an irregular mixture of both “Law” and “Service” naming strategies is observed.
 
-```{r fig-4-naming-strategies, fig.cap="Figure 4. Map of naming strategies"}
+```{r fig-4-naming-strategies, fig.cap="**Figure 4.** Map of naming strategies"}
 naming_strategies
@@
 As seen from Figure 4, few economic regions are characterized by a uniform naming strategy.
-In Volga-Vyatka economic region, “Law” strategy is the most prevalent among all the regions, with the exception of the Republic of Mari El.
+In the Volga-Vyatka economic region, the “Law” strategy is the most prevalent among all the regions, with the exception of the Republic of Mari El.
 In Volga and North Caucasus economic regions, service-based strategy is the prevailing approach in the majority of regions.
@@
 The findings of the study are somewhat contradictory.
-On the other hand, several hypotheses have been proven.
+On the one hand, several hypotheses have been proven.
 These include the following: law firm names in neighboring regions are more similar than law firm names in non-neighboring regions; the smaller the geographic distance between regions, the more similar the law firm names; and law firm names within an economic region are typically more similar compared to the law firm names outside an economic region.
@@
 The first of these represents a minority approach, while the remaining majority is divided between two other strategies.
-In the European South of Russia and in Volga economic region, “Service” is a dominant strategy.
+In the European South of Russia and in the Volga economic region, “Service” is a dominant strategy.
 However, no other spatial patterns in law firms naming have been identified.
-Economic regions are typically characterized by a mixture of naming strategies, expect for Volga-Vyatka, where “Law” strategy prevails, and Volga and North Caucasus, where “Service” strategy is dominant.
+Economic regions are typically characterized by a mixture of naming strategies, except for Volga-Vyatka, where the “Law” strategy prevails, and Volga and North Caucasus, where the “Service” strategy is dominant.
 
@@
 The findings demonstrate the effect of geographical proximity, neighboring, and economic relations on the similarity of the economic and, to a certain extent, cultural properties of the territories represented in firm names.
-The results generally align with the widely accepted classification of economic regions in Russia, although they highlight a few instances where a theoretically undesired internal heterogeneity within an economic region is evident.
+The results generally align with the widely accepted classification of economic regions in Russia, although they highlight a few instances where a theoretically undesired internal heterogeneity within an economic region is observed.
 Finally, the study provides an illustration of a semi-automated brand classification within a specific economic sector and discovers a geographical variation in naming strategies that could be further investigated.

### 2024-08-08 law-firms-names/journal-article/Script.R

@@ -9,13 +9,15 @@ library(stringr)
 library(tidyr)
 library(units)
 
-sf_use_s2(FALSE)
+sf_use_s2(FALSE) # disable to avoid errors in distances and intersections
 
+# Load the data
 data <- read_csv(here("../../ru-smb-companies/legal/panel.csv"))
 er <- read_csv(here("journal-article", "economic-regions.csv"))
-tiles <- read_csv(here("common", "russia-tiles.csv"))
-ru <- st_read(here("common", "ru.geojson"))
-ru_crs <- st_crs("+proj=aea +lat_0=0 +lon_0=100 +lat_1=68 +lat_2=44 +x_0=0 +y_0=0 +ellps=krass +towgs84=28,-130,-95,0,0,0,0 +units=m +no_defs")
+er_short_labels <- tibble(
+  economic_region = sort(unique(er$economic_region)),
+  label = c("C", "CC", "ES", "FE", "N", "NC", "NW", "U", "V", "VV", "WS")
+)
 org_forms <- c(
   "общество с ограниченной ответственностью",
   "общество с дополнительной ответственностью",
@@ -28,7 +30,11 @@ org_forms <- c(
   "полное товарищество",
   "товарищество на вере"
 )
+ru <- st_read(here("common", "ru.geojson"))
+ru_crs <- st_crs("+proj=aea +lat_0=0 +lon_0=100 +lat_1=68 +lat_2=44 +x_0=0 +y_0=0 +ellps=krass +towgs84=28,-130,-95,0,0,0,0 +units=m +no_defs")
+tiles <- read_csv(here("common", "russia-tiles.csv"))
 
+# Preprocess the data
 firms <- data %>% 
   filter(
     kind == 1, # companies only
@@ -60,37 +66,43 @@ firms <- data %>%
 unique_names <- distinct(firms, name)
 
 # Save unique names to a file for processing with YandexGPT API
-write_csv(
+if (get0("IS_PAPER", ifnotfound = FALSE)) {
+  write_csv(
   unique_names,
   glue("names-{strftime(Sys.time(), '%Y-%m-%d-%H-%M-%S')}.csv")
 )
+}
 
 # Load vectors obtained from YandexGPT API
 vectors <- read_csv(here("common", "names-vectors.csv"))
 
 # Clustering
 ## Find optimal number of clusters
-n_clusters <- 2:100
-scores <- sapply(
-  n_clusters, 
-  function(x) kmeans(
[…]

### 2024-08-08 law-firms-names/Paper.Rmd
Minor fixes before submission, #5

@@
 
-```{r imports, cache=TRUE, include=FALSE}
+```{r package-imports, include=FALSE}
+library(dplyr)
+library(ggplot2)
+library(glue)
 library(here)
+library(readr)
+library(readxl)
+library(sf)
+library(stringr)
+library(tidyr)
+library(units)
+```
+
+```{r data-imports, cache=TRUE, include=FALSE}
 source(here("journal-article", "Script.R"))
@@
 
-To address these challenges, a unified state registry of small and medium-sized businesses (SMB registry) may be used.
+To address these challenges, a unified state registry of small and medium-sized businesses (SMB registry) may be used [@SMBRegistry2024].
 The registry has been maintained since 2016 in accordance with Article 4.1 of the Federal Law of 24 July 2007 No.
@@
 
-The Yandex Foundation Models cloud service is used to transform the firm names into text vectors, or embeddings.
+The Yandex Foundation Models cloud service [@Yandex2024] is used to transform the firm names into text vectors, or embeddings.
 The “text-search-query” model is selected because its purpose, as stated in the documentation, is to vectorize short texts.

### 2024-08-08 law-firms-names/journal-article/Script.R

@@ -66,7 +66,7 @@ firms <- data %>%
 unique_names <- distinct(firms, name)
 
 # Save unique names to a file for processing with YandexGPT API
-if (get0("IS_PAPER", ifnotfound = FALSE)) {
+if (!get0("IS_PAPER", ifnotfound = FALSE)) {
   write_csv(
   unique_names,
   glue("names-{strftime(Sys.time(), '%Y-%m-%d-%H-%M-%S')}.csv")
